---
title: "Mobile Price Project"
author: "Xiaotang Tang, Jiayin Sun, Congyuan Xu, Yuantai Huang"
date: "4/24/2021"
output: html_document
---
1. Introduction:

For this project, our group is interested in the “Mobile Price Classification”. A new mobile company is starting it’s business, and this store wants to give tough fights to big companies like Apple, Samsung etc. The company founder Bob does not know how to estimate the price of mobiles that his company creates. In this competitive mobile phone market you cannot simply assume market prices for phones. To solve this problem Bob collects sales data of mobile phones from various companies.Bob wants to find out some relations between mobile phones’ features (eg:- RAM,Internal Memory etc) and selling prices. About this data set, there are 21 columns with 1000 of observations, the following are the descriptions for each variable:

*ID: The Ids.

*Battery_power: Total energy a battery can store in one time measured in mAh

*Blue: Has bluetooth or not

*Clock_speed: speed at which microprocessor executes instructions

*Dual_sim: Has dual sim support or not

*Fc: Front Camera megapixels

*Four_g: Has 4G or not

*Int_memory: Internal Memory in Gigabytes

*M_dep: Mobile Depth in cm

*Mobile_wt: Weight of mobile phone

*N_cores: Number of cores of processor

*Pc: Primary Camera megapixels

*Px_height: Pixel Resolution Height

*Px_width: Pixel Resolution Width

*Ram: Random Access Memory in Megabytes

*Sc_h: Screen Height of mobile in cm

*Sc_w: Screen Width of mobile in cm

*Talk_time: longest time that a single battery charge will last when you are

*Three_g: Has 3G or not

*Touch_screen: Has touch screen or not

*Wifi: Has wifi or not

And our team wants to foucs on exploring these following questions:

1.Is there any effect on 3G by the factor of 4G?
2.Is there any effect on Wifi by the factor of Bluetooth?
3.Is there any relationship between Battery power and the number of cores?
4.What factors affect the selling price most?

To get a better understanding of those SMART questions above, we would like to apply hypothesis tests and simple linear regression models to to accomplish this task.
```{r}
library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
library(dplyr)

setwd("/Users/sunemilyjiayin/Creative Cloud Files")
mobile.data <- read.csv("DS project_mobile.csv", header = TRUE)
print(mobile.data[is.na(mobile.data)])#Check if there are any null values in the dataset
```

```{r}
mobile.data$blue <- as.factor(mobile.data$blue)
mobile.data$dual_sim <- as.factor(mobile.data$dual_sim)
mobile.data$four_g <- as.factor(mobile.data$four_g)
mobile.data$n_cores <- as.factor(mobile.data$n_cores)
mobile.data$three_g <- as.factor(mobile.data$three_g)
mobile.data$touch_screen <- as.factor(mobile.data$touch_screen)
mobile.data$wifi <- as.factor(mobile.data$wifi)
mobile.data$price_range <- as.factor(mobile.data$price_range)
head(mobile.data)
```

```{r}
str(mobile.data)
```

2. EDA(Exploratory Data Analysis)

Before getting into the deep analysis about this dataset, we first cleaned the dataset by turning 8 variables to factors. We want to use boxplots to make exploritory data analysis (EDA).
```{r}

```

Is there any relationship between Battery power and the number of cores?
```{r}
mobile.data
```

```{r}
cor(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("pearson")))
cor(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("kendall")))
cor(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("spearman")))
cor.test(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("spearman")))
cor.test(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("pearson")))
cor.test(mobile.data$battery_power,as.numeric(mobile.data$n_cores,method = c("kendall")))
```

There is a correlation between Battery Power and Number of Cores
EDA
```{r}
#basic analysis
#plot of the battery power of number of cores
plot1<-ggplot(data = mobile.data, mapping = aes(x = n_cores,y = battery_power)) +
geom_point(aes(color=blue))+
  ggtitle("battery power and number of cores")
plot1
#histogram battery power vs. number of cores
plot2<-ggplot(data = mobile.data)+
geom_histogram(aes(x=battery_power,fill=n_cores),binwidth = 15)
plot2
plot3<-ggplot(data = mobile.data)+
geom_freqpoly(aes(x=battery_power,col=n_cores),binwidth=15)
plot3
#boxplot battery power by number of cores
plot4<-ggplot(data =mobile.data, mapping = aes(battery_power)) +
geom_boxplot(aes(col=n_cores))+
  ggtitle("boxplot battery power by number of cores")
plot4
```

```{r}
lm1<-lm(battery_power~n_cores,data=mobile.data)
summary(lm1)
lm2<-glm(battery_power~n_cores,data=mobile.data)
summary(lm2)
aov1<-aov(battery_power~n_cores,data=mobile.data)
summary(aov1)
```

```{r}
battery_core.table=xtabs(~battery_power+n_cores,data=mobile.data)
battery_core.table
```

```{r}
chisq.test(battery_core.table)
```






